Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-24 DGMM2025/paper.tex
Working on 4

    Let $V$ the visibility around the point $p$, let $c$ be the centroid of the
    visible points around p. The normal $\vec{n}$ is defined as the first
    eigenvector of the covariance matrix $\mathcal{V}$ of the visible points:
    \begin{equation}
        \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
    \end{equation}
    In order to reorient the normal, we use the trivial normal of the
    surface as a reference.

>>>>

    \newcommand{\Kernel}[1]{\ensuremath{w_{\sigma}(#1)}}
    We propose a new normal estimator on digital surfaces, which uses
    the visibility of the point of interest while taking into account
    a user-given scale $\sigma$. If $\sigma$ is proportionnal to the
    average length between visible points (so some $c\sqrt{h}$ for $c$
    some constant), then this estimator is observed to be multigrid
    convergent along digitization of smooth shapes. However, since the
    computation window is limited by the visibility, it better
    approximates the geometry near sharp or salient features.

    More precisely, we choose a Gaussian function
    $\Kernel{x}:=e^{-\frac{x^2}{2\sigma^2}}$ as a weight kernel. Let
    $V_p$ be the set of visible points from the point $p$.  Let $c_p$
    be the weighted centroid of the visible points around $p$,
    i.e. $c_p := \frac{\sum_{q \in V_p} \Kernel{\|q-p\|}q}{\sum_{q \in
        V_p} \Kernel{\|q-p\|}}$.  We form the weighted covariance matrix
    $\mathcal{V}_p$ of the points $V_p$ as:
    \begin{equation}
        \mathcal{V}_p = \sum_{q \in V_p} \Kernel{\|q-p\|}(q - c_p)(q - c_p)^T.
    \end{equation}
    The \emph{visibility normal} $\vec{n}_p$ of point $p$ is defined
    as the first eigenvector of the covariance matrix $\mathcal{V}_p$
    of the visible points, corresponding to its smallest
    eigenvalue. Its orientation is chosen so as to point in the same
    direction as the average of the trivial normals to the surfels
    touching the point $p$.

    %% Let $V_p$ be the set of visible points from the point $p$. Let
    %% $c_p$ be the weighted centroid of the visible points around $p$.
    %% The normal $\vec{n}$ is defined as the first eigenvector of the
    %% covariance matrix $\mathcal{V}$ of the visible points:
    %% \begin{equation}
    %%     \mathcal{V} = \frac{1}{\#V} \sum_{i=1}^{\#V} (p_i - c)(p_i - c)^T
    %% \end{equation}
    %% In order to reorient the normal, we use the trivial normal of the
    %% surface as a reference.
